The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-07 document/ms.tex
extrapolation

>>>>

For comparison, we repeated the analysis of \citet{Burke:2015} and fit a
double power-law occurrence rate to the short-period \kepler\ planet
candidates\footnote{The analysis was adapted from publicly available code that
was demonstrated to reproduce the same results as \citet{Burke:2015} by
\citet{Foreman-Mackey:2015a}.} and extrapolated to the center of the two
bins where we computed the occurrence rate.
At a period of 7~years and a radius of $0.2\,R_\mathrm{J}$, the extrapolated
occurrence is $0.73\pm0.28$ and at a radius of $0.6\,R_\mathrm{J}$, the
extrapolated rate is $0.15\pm0.05$.
